Super-resolution of Aeromagnetic Survey Data

### 2023-10-10 paper2.tex
Toward fixing paper 2
Uncomment that table at your own peril

\begin{figure}[hbt!]
    \begin{center}
        \includegraphics[width=0.75\linewidth]{fig/p2/temp_lr1.png}
        \includegraphics[width=0.75\linewidth]{fig/p2/temp_lr2.png}
    \end{center}
    \caption[Low-resolution geophysics grids]{
        The result of the proposed sampling and gridding on a selection of synthetic tiles loaded from the collection of \parencite{jessellNoddyverseMassiveData2022} at 4x scale.
        Note the coloured lines and accompanying tick marks in the ground-truth grid (GT, left) indicate cells which are sampled and used for gridding in the low-resolution grid (LR, right).
        High-resolution (HR, middle) is sampled and gridded from GT, with survey lines indicated by minor tick marks.
        The minimum curvature gridding process results creates a variety of low-resolution degradations.
    }
    \label{fig:lrdata}
\end{figure}
%TODO

@@

\section{Results}
\label{sec:2results}
Model performance is quantified using FSIM, and it is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids over the baseline model.

\begin{table}[hbt]
    \includegraphics[width=\linewidth]{fig/p2/temp_tbl.png}
    \begin{tabular}{ll}
                   & Reserved Synthetic Dataset & Reserved Aeromagnetic Dataset \\
                   & Mean / Standard Dev.       & Mean / Standard Dev.          \\
        \hline{}
        Baseline   & 0                          & 0                             \\
        Fine-Tuned & 0                          & 0                             \\
    \end{tabular}
    \caption[Accuracy Metrics]{Accuracy metrics for each upsampling method. The best performing method for each metric is bolded.}
    \label{tab:3metrics}
\end{table}

>>>>

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.75\linewidth]{fig/p2/temp_lr1.png}
    \includegraphics[width=0.75\linewidth]{fig/p2/temp_lr2.png}
    \caption[Low-resolution geophysics grids]{
        The result of the proposed sampling and gridding on a selection of synthetic tiles loaded from the collection of \parencite{jessellNoddyverseMassiveData2022} at 4x scale.
        Note the coloured lines and accompanying tick marks in the ground-truth grid (GT, left) indicate cells which are sampled and used for gridding in the low-resolution grid (LR, right).
        High-resolution (HR, middle) is sampled and gridded from GT, with survey lines indicated by minor tick marks.
        The minimum curvature gridding process results creates a variety of low-resolution degradations.
    }
    \label{fig:lrdata}
\end{figure}
%TODO

@@

\section{Results}
\label{sec:2results}
Model performance is quantified using FSIMi in Cref{tab:2metrics}, and it is seen that fine-tune training increases FSIM score for the task of super-resolution for aeromagnetic grids over the baseline model.

% \begin{table}[hbt]
% %     % \includegraphics[width=\linewidth]{fig/p2/temp_tbl.png}
% % \begin{tblr}{ll}
% %                 & Reserved Synthetic Dataset & Reserved Aeromagnetic Dataset \\
% %                 & Mean / Standard Dev.       & Mean / Standard Dev.          \\
% %     \hline{}
% %     Baseline   & 0                          & 0                             \\
% %     Fine-Tuned & 0                          & 0                             \\
% % \end{tblr}
%     \caption[Accuracy Metrics]{Accuracy metrics for each upsampling method. The best performing method for each metric is bolded.}
%     \label{tab:2metrics}
% \end{table}
